### 2023-10-31 README.Rmd
add code

>>>>

On beluga, we use the apptainer iamge instead.

```{bash eval=FALSE}
. /workspace/conda/etc/profile.d/conda.sh 
. /workspace/conda/etc/profile.d/mamba.sh
PATH="$PATH:$HOME/.local/bin"
mamba activate cameratraps-detector
rofcamtrap/scripts/bash/camtrap.sh -b "/workspace/git" -s "/workspace/storage/my_passport_images" -m "/workspace/models/md_v5a.0.0.pt" md

$ mkdir -p /scratch/$USER/apptainer/{cache,tmp}
$ export APPTAINER_CACHEDIR="/scratch/$USER/apptainer/cache"
$ export APPTAINER_TMPDIR="/scratch/$USER/apptainer/tmp"

salloc --time=00:05:00 --mem=4G --ntasks=1 --gpus-per-task=1 --cpus-per-task=1 --account=rrg-fstewart

apptainer shell --nv -C -B "$(pwd):/workspace/rofcamtrap"  -B "/media/vlucet/TrailCamST/TrailCamStorage:/workspace/storage/TrailCamStorage"  -B "/media/vlucet/My Passport/Images:/workspace/storage/my_passport_images" rofcamtrap.sif

apptainer shell --nv -C -B "$(pwd):/workspace/rofcamtrap" -B "/home/vlucet/projects/rrg-fstewart/vlucet:/workspace/project/" rofcamtrap.sif
```
